University of Florida Knowledge Base Acceleration Notebook

### 2013-10-25 paper/flairs27/content/abstract.tex
added the paper for FLAIRS27. It needs a LOT of work

In this paper we will present the system design and algorithm adopted by the 
GatorDSR team, University of Florida to efficiently process TREC KBA 2013 --- 
SSF track. Here we will describe the system evolution as well as the details 
of our algorithm to extract slot values for the given slot name. Scalability 
and efficiency in precision and recall are the major goals of this work, 
given the overly limited time limitation and available computational resources.

>>>>

In this paper we will present the system design and algorithm adopted by the 
GatorDSR team, University of Florida to efficiently process TREC KBA 2013 --- 
SSF track. Here we will describe the system as well as the details 
the algorithms used to extract slot values for the given slot name. Scalability, efficiency, precision and recall are the major goals of this work, 
given the overly limited time limitation and available computational resources.

### 2013-10-25 paper/flairs27/content/implementation.tex
added the paper for FLAIRS27. It needs a LOT of work

The procedure to extract slots with the patterns is to 
first find Streamitems that contain the
entities by using alias names of the entities. Next, inside these Streamitems, 
fetch the sentences which contain entities by using alias names and the 
coreference information provided by Lingpipe tags. Use these sentences to 
match existing patterns, and when patterns matched, generate SSF results.

\begin{algorithm}
  \caption{Streaming Slot Value Extraction Pseudocode}
  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
  \textbf{List of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
  \begin{algorithmic}%[1]
    \FOR{$si \in \mathcal{S}$}
      \FOR{$sentence \in si$}
        %%\IF{check\_pattern(sentence, pattern)}
        \FOR{$pattern \in P$}
          \IF{Satisfies($sentence$, $pattern$)}
            \STATE Emit($sentence$, $pattern$) // Deal specifically with the three types
          \ENDIF
        \ENDFOR
      \ENDFOR
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

\subsubsection{Types of patterns}
A pattern is defined as a record representing knowledge going to be added to a knowledge base.
A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.

The first value, $p_1$ represents the type of entity. These entity types are in
the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
represents a person.
The $p_2$ represents a slot name.
A list of slot names is present in Table~\ref{table:slotNameOntology}.
The third element $p_3$ is the pattern content. This is a string found in the sentence.
The extractor looks for this exact string or pattern in a sentence.
The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
$p_4$ to explore sentence.
The final element $p_5$ represent the slot value of a pattern. Thois
%When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity 
type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
For these three kinds of patterns, we implement them in different 
ways accordingly. Next, we explain the patterns with more details, an
example can be found in Figure~\ref{fig:pattern}.

@@

We sampled documents from the training data period to generate an initial set of patterns. We then use these patterns to generate SSF results. By manully looking at these results, we prune some patterns with poor­performance and add more patterns that we identified from these results. We use several iterations to find the best patterns. We found that it is time consuming to identity quality pattern.

>>>>

With the Streamitem indexes generated by the CCR, we first fetch the sentences containing entites
by using alias names and coreference information provided by Lingpipe tags. Then use these senteces 
to match patterns and when patterns matched, generate SSF results.

\begin{algorithm}
  \caption{Streaming Slot Value Extraction Pseudocode}
  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
  \textbf{List of streamitems containing entities $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\

  \begin{algorithmic}%[1]
    \FOR{$si \in \mathcal{S}$}
      \FOR{$sentence \in si$}
        \FOR{$entity \in \mathcal{E}$}
	  \IF{Contains($sentence$, $entity$)}
          %%\IF{check\_pattern(sentence, pattern)}
            \FOR{$pattern \in P $ suitable for $entity$} 
              \IF{Satisfies($sentence$, $pattern$)}
                \STATE Emit($sentence$, $pattern$)
              \ENDIF
	    \ENDFOR
          \ENDIF
        \ENDFOR
      \ENDFOR
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

\subsubsection{Format of patterns}
A pattern is defined as a record representing knowledge going to be added to a knowledge base.
A pattern $\mathcal{P}$ is represented as a five-tuple $\mathcal{P} = \langle p_1, p_2, p_3, p_4, p_5 \rangle$.

The first value, $p_1$ represents the type of entity. These entity types are in
the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
represents a person. \texttt{FAC}, \texttt{ORG} and \texttt{PER} are Lingpipe entity types.
The $p_2$ represents a slot name.
A list of slot names is present in Table~\ref{table:slotNameOntology}.
The third element $p_3$ is the pattern content. This is a string found in the sentence.
The extractor looks for this exact string or pattern in a sentence.
The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
$p_4$ to explore sentence.
The final element $p_5$ represent the slot value of a pattern. Thois
%When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity 
type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
For these three kinds of patterns, we implement them in different 
ways accordingly. Next, we explain the patterns with more details, an
example can be found in Figure~\ref{fig:pattern}.

\subsubsection{Types of patterns}
There are three types of patterns distinguished by different types of slot values in the patterns. 
The matching methods using these three types of patterns are implememented according to the different information and structures of slot values.

@@

\subsubsection{A short discussion}
We sampled documents from the training data period to generate an initial set of patterns. We then use these patterns to generate SSF results. By manully looking at these results, we prune some patterns with poor­performance and add more patterns that we identified from these results. We use several iterations to find the best patterns. We found that it is time consuming to identity quality pattern.

### 2013-10-25 paper/flairs27/content/introduction.tex
added the paper for FLAIRS27. It needs a LOT of work

An important challenge in maintaining Wikipedia.org (WP), the most popular 
web-based, collaborative, multilingual knowledge base on the internet, is  
making sure its contents are up-to-date. Presently, there is considerable time lag 
between the publication date of cited news and the date of an edit to WP 
creating the citation. The median time lag for a sample of about 60K
web pages cited by WP articles in the \textit{living\_people} category is over 
a year and the distribution has a long and heavy tail~\cite{JFrank12}. 
Also, the majority of WP entities have updates on their associated article much 
less frequently than their mention frequency. Such stale entries 
are the norm in any large knowledge base (KB) because the number of humans 
maintaining the KB is far fewer than the number of entities. 
%Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
Reducing latency keeps KBs such as WP relevant and helpful it users.

>>>>

An important challenge in maintaining Wikipedia.org (WP), the most popular 
web-based, collaborative, multilingual knowledge base on the internet, is  
making sure its contents are up-to-date. Presently, there is considerable time lag 
between the publication date of cited news and the date of an edit to WP 
creating the citation. The median time lag for a sample of about 60K
web pages cited by WP articles in the \textit{living\_people} category is over 
a year and the distribution has a long and heavy tail \cite{JFrank12}. 
Also, the majority of WP entities have updates on their associated article much 
less frequently than their mention frequency. Such stale entries 
are the norm in any large knowledge base (KB) because the number of humans 
maintaining the KB is far fewer than the number of entities. 
%Further, the number of mentions is much larger than the number of entities~\cite{JFrank12}. 
Reducing latency keeps KBs such as WP relevant and helpful it users.
